1. Object x <-1:15
Construct a 5x3 matrix for the value of x.
```{r}
x <- matrix(1:15, nrow = 5, ncol =3);
x
```



2. Write a program to generate the following 4x4 matrix
0 0 0 0
0 0 0 0
0 0 0 0

```{r}
x <- matrix(0, nrow = 4, ncol = 4);
x;
```


3. The object x<-1:8
Write a program to generate the following 3x8 matrix using "cbind(),rbind(),rev(),rep()"
1 2 3 4 5 6 7 8
8 7 6 5 4 3 2 1
3 3 3 3 3 3 3 3
```{r}
x <- c(1:8);
m <- rbind(x,rev(x),rep(3));
m;
```


4. Chose two different(x,y) 4x4 matrix to perform the following arithmetic operations
create matrix:
```{r}
x <- matrix(1:16, nrow = 4 , ncol=  4, byrow = T);
y <- matrix(16:1, nrow = 4 , ncol=  4, byrow = T);
```



(a). x + y
Answer:
```{r}
x + y

```


(b). x - y
```{r}
x - y
```


(c). x*y
```{r}
x * y
```


(d). x%*%y
 
```{r}
x%*%y
```
 

(e). Difference between (c) &(d)
-(c):take each corresponding element from matrix x and y, and multiply those elements together.take each corresponding element from matrix x and y, and multiply those elements together.
-(d):this inner product of two matrixs.

(f). Inverse of y
by using matlib library package we can use inv() built-in function
but matrix can be inverse only if det(x)!=0
so we should check matrix det first
```{r}
det(y);


```
det(y)= 0 so matrix have no inverse

```{r}
i <- inv(y)
i
```



(g). z<-x/y

```{r}
z <- x/y
z

```

(h). Transpose of z

```{r}
t <- t(z)
t
```

(i). Diagonal of transpose matrix

```{r}
d <- diag(t)
d
```

5. Difference between (i) & (ii)
(i) the matrix is created by filling the value from Vector by row fist
(ii) the matrix is created by filling the value from vector by col fist

6. Which function can we use for inner product and outer product in matrix calculation?
Answer:
Function for inner product is %*%
Function for outer product is %o%

7. Explain the use of all.equal() function in Matrix with a sample program.
Answer:
all.equal() function in Matrix is used to compare the 2 matrix to check that 2 matrix is nearly equal or exactly equal or not and return mean of the different.

```{r}
all.equal(x,x)
all.equal(x,y)

```



8. Explain the use of dim() function with a sample program.

dim() function is used to get the dimensions of matrix. It return 2 integer number that the fist one indicate number of row and second number indicate number of column.

```{r}
dim(y)
```

9. Use of $ operator, and square brackets [] in List with example program.
- $ operator in List is used for access the Element in the list by name.
-[] square brackets operator in List is used for access the element in the List by index.

```{r}
batch4 <- list(student = 41, semester = 7, sub1 = "ielts", sub1 = "ob", sub3 = "ds", active = T);

"use $ operator"
batch4$student
batch4$active
"use [] operator"
batch4[2]
batch4[-1]
```

10. Explain ifelse() with example.
This is a shorthand function to the traditional if ... statements

```{r}
num <- 44;
ifelse(num %%2 != 1, "odd", "even")
```

11. Write a program to get the weight and height from the user to calculate the following cases
a. If your BMI is less than 18.5, it falls within the underweight range.
b. If your BMI is 18.5 to <25, it falls within the normal.
c. If your BMI is 25.0 to <30, it falls within the overweight range.
d. If your BMI is 30.0 or higher, it falls within the obese range.

```{r}
weight <- as.numeric(readline(prompt="Enter weight (kg): "))
height <- as.numeric(readline(prompt="Enter height (m): "))
bmi <- weight/height^2
ifelse(bmi<18.5, "underweight range", ifelse(bmi<25, "normal range", ifelse(bmi< 30, "overweight range", "obese range")))

```

12. Difference between List and Data frame with an example program.
-List is the array of element of same or different type that store in sequence.
-Data Frame is the matrix of the same or different type that store in the form of row and column.
```{r}
#list
list(student = 41, semester = 7, sub1 = "ielts", sub1 = "ob", sub3 = "ds", active = T);
```


```{r}

#data frame
letter <- c("a", "b", "c", "d");
number <- c(1, 2, 3, 4);
data.frame(letter=letter, number = number)
```


13. Difference between repeat and while loop with example program.

-Repeat is the loop that requires you to explicitly break the loop on your own and can be at any point in the body of the loop.
-While is the loop that tests a condition to determine when to finish looping.
```{r}
#Repeat
"Repeat"
i <- 0
repeat {if (i==3) break;print(i);i<-i+1}
```


```{r}

#while
"While"
j <- 0
while (j!=3) {print(j);j<-j+1}
```

