```{r}

data <- ggplot2 :: mpg
data


```
a. add new column Transmission
#using ggplot2
```{r}
data$Transmission <- ifelse(startsWith (data$trans, 'a'), 'automatic', 'manual')

names(data)

head(data)
```

b.plot the graph between cty and hwy
```{r}
plot <- ggplot(data, aes(x= cty, y= hwy))
plot
```


c. x-axis title: City Mile per Galion Text in Green color, bold and center, size=15,
space b/w text and graph: 25
```{r}
x_plot_title <- plot + xlab('City Mile per Galion')

x_plot_title <- x_plot_title + theme(axis.title.x = element_text(size = 15, color = 'green', face='bold', margin=margin(r=25)))

x_plot_title

```
d. y-axis title: Highway Miles per GallonText in Blue color, bold and center, size=15, space b/w text and graph: 30
```{r}
y_plot_title <- plot + ylab('Highway Miles per GallonText')

y_plot_title <- y_plot_title + theme(axis.title.y = element_text(size = 15, color = 'blue', face='bold', margin=margin(r=30)))

y_plot_title
```

plot_view
```{r}
plot_view <- plot + ylab('Highway Miles per GallonText') + xlab('City Mile per Galion') + theme(axis.title.y = element_text(size = 15, color = 'blue', face='bold', margin=margin(r=30))) + theme(axis.title.x = element_text(size = 15, color = 'green', face='bold', margin=margin(r=25)))

plot_view

```
e. Create a subplot in a graph between Transmission and year


```{r}
sub_plot <- plot_view + facet_grid(Transmission ~ year) 
sub_plot

```

f. Draw heights of the bars to represent values in the data, each bar's border is in blue color and fill with yellow color using geom_col()
```{r}
sub_plot <- sub_plot+ geom_col(fill='yellow', color='blue', face='bold')
sub_plot
```

g. Graph rectangular box border is in red color and fill with blue
```{r}
sub_plot <- sub_plot + theme(strip.background = element_rect(color="red",fill='blue'))
sub_plot
```

h. Graph title : Fuel economy data from 1999 to 2008
Text color : Green, size: 20, center, bold
```{r}
sub_plot <- sub_plot + ggtitle('Fuel economy data from 1999 to 2008') + theme(plot.title = element_text(size=20 , color ='green', face ='bold', hjust = 0.5))
sub_plot

```
