1. Calculate the following
a.sum(...) with and without loop.
```{r}
#without loop
a <- 5:100

sum(a^4 + 5*a^3)



```

```{r}
#with loop
b <- 0
for(i in 5:100) {
  b = b + (i^4 + 5*i^3)
}
b
```
b.Calculate U40 which is a series,Un = Un-1 +Un-2 , with U1= 1 and U2= 2 ?

```{r}
u1 <- 1
u2 <- 2
u3 <- 0
for (j in 3:40) {
  u3 = u1 + u2
  u1 = u2
  u2 = u3
  print(u3)
}

u40= u3
u40
```
c. Write a program to calculate cos x, sin x(Taylor series) , Get the input(x) from the user
and n=45.
```{r}
# way 1

x <- as.numeric(readline(prompt="Enter value x: "))
n = 45
cosn = 0
sinn = 0
cosx = 0
sinx = 0


for (i in 0:n) {
  cosn = (-1^n) * (x^(2*n))/ factorial(2*n)
  cosx = cosx +  cosn
  sinn = -1^(n) * x^(2*n + 1)/ factorial(2 * n + 1)
  sinx = sinx +sinn
}



cosx
sinx
```

```{r}
# way 2 using pracma package
#the maximum of n = 8
x <- as.numeric(readline(prompt="Enter value to x: "))
n = 4
sinx = taylor(sin , x , n)
cosx = taylor(cos , x , n)
sinx
cosx

```

```


d. Create a vector of the values of e^x cos(x) at x = 3, 3.1, 3.2, . . . , 6.

```{r}
x = seq(3,6 , by=0.1)
d <- c(exp(x) * cos(x))
d

```



e. use x <- 1:300. How many numbers in x are divisible by 2?


```{r}
x <- 1:300
count <- 0
for (k in x){
  if(k %% 2 == 0){
    count=count+1
  }
}
count
```

2.2. Solve the following system of linear equations using Gaussian elimination (Ax=y)
x + 2y + 3x = 9

2x - y + 2z = −3

3x + 3y + z = 5

```{r}
#by using matlib package

A <- matrix(c(1, 2, 3,
            2, -1, 2,
            3,  3, 1), 3, 3, byrow=TRUE)
A

B <- c(9, -3, 5)

result <- gaussianElimination(A, B)
result
paste(" x =",result[10], "y =",result[11], "z =",result[12])

```


3. Use outer function to create the following matrix

```{r}
r <- 0:4
c <- 0:4
outer(c, r, "+2")

```


4.Get the COVID-19 Dataset from the data sources. Number of observations should be more than
100.Then, report the following informations

a. Data Source detail(Ex: Link)
https://www.ecdc.europa.eu/sites/default/files/documents/COVID-19-geographic-disbtribution-worldwide.xlsx

b. Explain the Unit & Necessity of each variable
```{r}

#by using tidyverse package
COVID_19_geographic_disbtribution_worldwide <- read_excel("C:/Users/lycha/Downloads/COVID-19-geographic-disbtribution-worldwide.xlsx")

covid_data <- COVID_19_geographic_disbtribution_worldwide

covid_data

names(covid_data)

```

c.Find the missing values(rows & columns) and replace them with mean(Tidy Dataset)
```{r}
covid_data[] <- lapply(covid_data, function(x) { 
  x[is.na(x)] <- mean(x, na.rm = TRUE)
  x
})
#all cell data is exist value
covid_data
is.na(covid_data)

```
d.Generate the two new variables(Var1:Mean, Var2: Median from available variable)

```{r}

covid_data %>% mutate(Mean=mean(cases),Median=median(cases))



```

e. Rename the two existing variables 
```{r}
covid_data %>% rename(Day=day, Months=month,)


```
f. Create a plot using following instructions (using 7 layers of Grammar of Graphics)
  i. Choose x and y axis(aes)
  
```{r}
# Choose Date as X and TotalCases of covid as Y
data <- covid_data %>% group_by(dateRep) %>% count(dateRep, wt = cases)


data

date <- data[['dateRep']]

cases <- data[['n']]

data


```
  
  ii.geom_point() - specify the parameters, size : 5, color: red, alpha: 1⁄5
  
```{r}
#using ggplot2 package
gp = geom_point(alpha=1/5, color="red", size=5)

gp

p <- ggplot(x = data, mapping = aes(x = date, y = cases)) + gp

p


```
  
   iii. Use Facet grid, cartesian coordinates & geom_smooth() 
   
```{r}
# facet_grid

p + facet_grid(date)

p

```


```{r}
# coord_cartesian
p + coord_cartesian(expand = FALSE)

```


```{r}
#geom_smooth
p + geom_smooth()

```

iv. Assign the title to x, y and graph
  
```{r}

p <- p + ggtitle("Covid-19 statistic:") + xlab("Date") + ylab("Total Cases")
p

```

v. Export the graph to your working directory with the title called “covid_19_ dataset.png”
```{r}
ggsave(filename = "D:/covid_19_dataset.png", units = "cm", width = 40, height = 25)

```

