1. Write a R code to Generate 6X6 matrix (A) using the random numbers between 1 to 100
&amp; generate another 6x6 matrix (B) using random numbers between 500 to 600.

```{r}
A <- matrix(sample(1:100), 6,6)
B <- matrix(sample(500:600),6,6)

A
B

```
a. Find the range of matrices A and B.
```{r}
#rangeA
range(A)
#rangeB
range(B)
```



b.Find the max value from each row of the matrices A and B.
```{r}
#maximum of matrix A
max(A)
#maximum of matrix B
max(B)

```
c. Find the diagonal values of matrices A&amp;B.

```{r}
#diagonal of matrix A
diag(A)
#diagonal of matrix A
diag(B)

```
d. Multiply matrices A and B
```{r}
#mutiply of matrices A nad B
A %*% B

```

e.Replace the 4th row of Matrix A with diagonal values of matrix B
```{r}
rbind(B)
B

```



f.Multiply matrices A &amp; B and store the values on X.
```{r}
X <- A %*% B
```

g.Divide the matrix A with matrix B.
```{r}
A/B
```




2. Create a table using dataframe/tibble with the following categories(a to f) (10 marks)

a. First name,
b. Second Name,
c. Age,
d. Occupation,
e. Place,
f. Random numbers( between 1 to 10)

And input at least 10 samples(observation) and do the following

g. Extract the last column (f)

h. Find the sum, mean and length of the extracted column

```{r}
fname <- c('ly', 'kaing', 'hoeurng', 'ley' , 'sang', 'daro', 'chea', 'han', 'hy', 'heng')
sname <- c('chandara', 'sokheng', 'hen','kimteng','sonyratt','dalya', 'nataly', 'manich', 'chayrith', 'senghak')
age <- c(20,21,21,21,21,19,22,21,23,25)
occu <- rep(c('student', 'doctor','teacher'),3,10)
pla <- rep(c('A', 'B','C'),3,10)
num <- sample(1:10)

data_frame <- data.frame(first_Name = fname, Second_Name= sname, Age= age, Occupation= occu, Place=pla,Number=num)
data_frame
```



g. Extract the last column (f)
```{r}
f<- transmute(data_frame, Number)
f

```

h. Find the sum, mean and length of the extracted column
```{r}
#sum
sum(f)
#mean
mean(f$Number)
#length
length(f)

```

4. Find the assigned Dataset from the list below and perform the following (20 Marks)
a. Import and Clean the dataset.

```{r}
my_data <- read_csv("D:/R/elo_blatter.csv")


my_data

is.na(my_data)

my_data[] <- lapply(my_data, function(x) { 
  x[is.na(x)] <- mean(x, na.rm = TRUE)
  x
})
```



b. Find the x and y variables(axis) from the assigned dataset and give the reason for
selecting the x and y axis


- I choose country as X axis and elo15 as Y axis.because it can display the elo15 statistic to the coutry 
```{r}
plot_data <- ggplot(my_data, mapping=aes(x = country, y=elo15))
plot_data
```

the

c. Plot the graph using geom_col() and perform the linear model in statistics.

```{r}
plot_col <- plot_data + geom_col()

plot_col

plot_data +  geom_smooth(method = "lm")
```


d. Perform the facet with the available columns(Choose the any two variables from the
columns)

```{r}

facet_plot = plot_col + facet_grid( gdp_source ~ confederation)
facet_plot
```


e. Use the theme layer to do the following (Note: Based on dataset, name the x and y axis &amp;
graph)


e.1. x-axis title =“________”, Size=10, Bold, Text in Green color, Center, space
between graph and title = 20.

```{r}
plot_title <- facet_plot + xlab("_______") +  theme(axis.title.x = element_text(size = 25, color = 'green', face='bold', margin=margin(r=20)))
plot_title
```



e.2. y-axis title =“________”, Size=10, Bold, Text in Yellow color, Center, space
between graph and title = 20.


```{r}
plot_title <- plot_title + ylab('________') +  theme(axis.title.y = element_text(size = 10, color = 'yellow', face='bold', margin=margin(r=20)))
plot_title
```

e.3. Graph title =”_________”,Size = 25, Bold, Center, Text in Blue color, space
between graph and title = 25.

```{r}
plot_title <- plot_title + ggtitle('________') + theme(plot.title = element_text(size=25 , color ='blue', face ='bold', hjust = 0.5))

plot_title
```



3. Create a .txt file (Minimum : 150 words) with the latest news (In English) in cambodia from
the official news agency’s website(Note: Include the reference link) and do the following
(20 Marks)

a. Read the .txt file

data link:https://www.phnompenhpost.com/national/public-urged-adopt-healthier-habits

```{r}
read_text = read_file("D:/R/hot_news.txt")
read_text

class(read_text)
```



#b. Perform the Tokenization count the words

#c. 
```{r}
words_data <- paste0(read_text)

tokens <- tokenize_words(words_data)

count <- count_words(words_data)

count

```

#c. Identify the most repeated word and replace that word with “KIT”
#Identify the most repeated word

```{r}
most_words <- names(table(tokens))[as.vector(table(tokens))==max(table(tokens))]
most_words_count <- max(table(tokens))
print("The Most repeated word is: ")
most_words
print("repeated for:  ")
most_words_count
```



```{r}
#replace that word with “KIT”
subs <- gsub(most_words, "KIT", words_data)
subs
#d. Perform the Sentiment analysis
library(sentimentr)
# To display the sentences
result1<- get_sentences(subs) 
result1



```

```{r}


#d. Perform the Sentiment analysis
library(sentimentr)
# To display the sentences
result1<- get_sentences(subs) 
result1
#number of sentences and words(Sentiment at the sentence level)
result2<- sentiment(subs) # To know 
result2
# Aggregated sentiment group by each sentiment
result3 <-sentiment_by(subs) 
result3
# Emotion at the sentence level one by one
result4<- emotion(subs) 
result4
# Aggregated emotion group by emotion
result5<- emotion_by(subs) 
result5
# Profanity at the sentence level
result6<- profanity(subs) 
result6
# Aggregated profanity by group(s)
result7<- profanity_by(subs) 




```




d. Perform the Sentiment analysis

e. Plot the graph between “words count” and “words” using geom_col()

e.1. X-axis title =“Number of words”, Size=10, Bold, Text in Blue color,
Center, space between graph and title = 20.




















